---
title: "`r packageDescription('Tristyly')[['Title']]`"
author: "`r packageDescription('Tristyly')[['Author']]`"
date: "Updated: 2016-11-24; Processed: `r Sys.Date()`"
output:
  html_document:
    toc: true
vignette: >
  % \VignetteIndexEntry{Stochastic Simulation of Tristyly Genentic Polymorphism}
  % \VignetteEngine{knitr::rmarkdown}
---

```{r setup, echo=FALSE}
suppressPackageStartupMessages({
    library(Tristyly)
})
```

# Methods

## Genetics

The genetics are summarized by the relationship between genotypes and
the gametes produced. The data object `G0` represents gametes produced
in the absence of recombination between loci, `G1` the gametes
produced in the presence of free recombination.

```{r genetics}
library(Tristyly)
genetics
G0          # complete linkage
G1          # free recombination
```

Arbitrary recombination between loci occurs at rate `r`, with gamete
frequencies summaried by the function `G()`:

```{r recombination}
G <- G(0.1)     # e.g., recombination between loci = 0.1
```

Initial genotype frequencies are given by a vector `gtype`, e.g.,

```{r gtype-1}
gtype <- gtype_init()    # approximate isoplethy
gtype
```

Inputs do not have to be frequencies

```{r gtype-2}
gtype_init(c(sm_sm=100, sM_sm=70, sM_sM=20, Sm_sm=50))
```

Gamete frequencies prior to mating at the genotype level are

```{r gamete}
gametes(gtype, G)
```

and at the morph level

```{r gamete-morph}
gametes_by_morph(gtype, G)
```

## Mating

