---
title: "`r packageDescription('Tristyly')[['Title']]`"
author: "`r packageDescription('Tristyly')[['Author']]`"
date: "Updated: 2016-11-26; Processed: `r Sys.Date()`"
output:
  html_document:
    toc: true
vignette: >
  % \VignetteIndexEntry{Stochastic Simulation of Tristyly Genentic Polymorphism}
  % \VignetteEngine{knitr::rmarkdown}
---

```{r setup, echo=FALSE}
suppressPackageStartupMessages({
    library(Tristyly)
})
```

# TODO

- test morph-specific fertility
- perennial populations
- self-fertilization

# Methods

## Genetics and mating

The genetics are summarized by the relationship between genotypes and
the gametes produced. Arbitrary recombination between loci occurs at
rate `r`, with gamete frequencies summaried by the function `G()`:

```{r recombination}
G <- G(0.1)            # e.g., recombination between loci = 0.1
```

Mating is summarized by a matrix `M()` where entries i, j correspond
to male fertility of morph j on female of morph i. Row sums correspond
to differences in female fertility, column sums to differences in male
fertility.


```{r mating}
M()
```

Approximately isoplethic genotype frequencies are given by
`isoplethy()`; using an optional argument `N` creates a sample of size
`N` from an isoplethic population.

```{r gtype-1}
isoplethy()
isoplethy(100)
```

Arbitrary starting vectors are possible using `as_genotype()`

```{r gtype-2}
as_genotype(c("sm/sm"=100, "sM/sm"=70, "sM/sM"=20, "Sm/sm"=50))
```
Morph frequencies are summarized with `morph_frequency()`

```{r gamete-morph}
morph_frequency(isoplethy(30))
```

## Iteration

The `iterate_*` functions take an initial population and iterate it
until a specific stopping criterion is met. `plot_iterations()`
visualizes the result; the starting population is represented by a
solid dot.

```{r iterate, fig.asp=1}
tbl <- iterate_stochastic(isoplethy(50), 100)
tbl
tail(tbl)
plot_iterations(tbl)

set.seed(1234L)
tbl <- iterate_deterministic(isoplethy(3), , tolerance=1e-4)
plot_iterations(tbl)
```

The `iterate_to_dimorphism()` function repeatedly iterate a single
population until loss of one morph.

```{r iterate-to-dimorphism}
tbl <- iterate_to_dimorphism(isoplethy(20), times=100)
table(tbl$Morph_lost, useNA="ifany")
plot(log10(Generation) ~ Morph_lost, tbl)
```

## Replication

The `replicate_to_dimorphism()` function iterates independent
populations to loss of one morph.

```{r replicate_to_dimorphism}
tbl <- replicate_to_dimorphism(N=20, times=100)
table(tbl$Morph_lost) / nrow(tbl)
plot(ecdf(tbl$Generation),
    xlab="Generation", ylab="Cummulative Probability",
    main="Time to Loss")
```
