---
title: "`r packageDescription('Tristyly')[['Title']]`"
author: "`r packageDescription('Tristyly')[['Author']]`"
date: "Updated: 2016-11-24; Processed: `r Sys.Date()`"
output:
  html_document:
    toc: true
vignette: >
  % \VignetteIndexEntry{Stochastic Simulation of Tristyly Genentic Polymorphism}
  % \VignetteEngine{knitr::rmarkdown}
---

```{r setup, echo=FALSE}
suppressPackageStartupMessages({
    library(Tristyly)
})
```

# Methods

## Genetics

The genetics are summarized by the relationship between genotypes and
the gametes produced. Arbitrary recombination between loci occurs at
rate `r`, with gamete frequencies summaried by the function `G()`:

```{r recombination}
G <- G(0.1)            # e.g., recombination between loci = 0.1
```

Approximately isoplethic genotype frequencies are given by
`isoplethy()`; using an optional argument `n` creates a sample of size
`n` from an isoplethic population.

```{r gtype-1}
isoplethy()
isoplethy(100)
```

Arbitrary starting vectors are possible using `as_genotype()`

```{r gtype-2}
as_genotype(c("sm/sm"=100, "sM/sm"=70, "sM/sM"=20, "Sm/sm"=50))
```

Gamete frequencies prior to mating at the genotype level are

```{r gamete}
gamete_frequency(isoplethy(), G)
```

and at the morph level

```{r gamete-morph}
gamete_frequency_by_morph(isoplethy(), G)
```

## Mating

